---
title: "GeoCode and Reverse GeoCode API"
author: "Aashana, Jasleen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# GeoCode and Reverse GeoCode API 


## Overview

This package has a geoCode.R file which has two functions. Named latlon and reverselatlon.

* latlon

This function calls the google geocode API https://developers.google.com/maps/documentation/geocoding/start 

To run this you need get your own API key from google, which can be taken form the link above. The functions needs two arguments address and apikey. and returns lat and long of the address in a Vector.

```{r}
latlon <- function(address, apiKey){

  param <- gsub("[\\@\\#\\%\\&\\!\\(\\)\\_\\*\\+\\;\\^]", "", address)
  params <- trimws(gsub("\\s+","+", param))

  base <- "https://maps.googleapis.com/maps/api/geocode/json?address="
  
  urlAPI <- paste0(base,params,"&key=",apiKey)
  callAPI <- GET(urlAPI)
  content(callAPI)
  resultJSON <- fromJSON(txt = callAPI$url)
  X <- resultJSON$results$geometry$location$lng
  Y <- resultJSON$results$geometry$location$lat

  return(c(X,Y))
}
```

* reverselatlon

This function also call google geocode but reverse geocode this function needs three arguments. The lat, long, and apikey. It returns the address of the given lat long. 

```{r}
reverselatlon<- function(lat, lon, apiKey){

  params <- paste0(lat,",",lon)
  base <- "https://maps.googleapis.com/maps/api/geocode/json?latlng="
  
  urlAPI <- paste0(base,params,"&key=",apiKey)
  callAPI <- GET(urlAPI)
  content(callAPI)
  resultJSON <- fromJSON(txt = callAPI$url)
  address <- resultJSON$results$formatted_address
  
  return(address)
}
```

